Artin Group Presentations Arising from Cluster Algebras

### 2014-09-25 Paper.tex
New Paragraph

\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to motivate our own results. For further definitions and references on the topic, we refer the reader to \cite{FZ02}. Section \ref{sec:finite-type_diagrams} will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles. In Section \ref{sec:defn_artingroup}, we define the appropriate relations for our Artin group presentations. Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles. Section \ref{sec:main_result} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$. Finally, in Section \ref{sec:affine}, we will state a conjecture which could extend the main result to diagrams of affine type. \\

>>>>

\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to motivate our own results. For further definitions and references on the topic, we refer the reader to \cite{FZ02}. Section \ref{sec:finite-type_diagrams} will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles. In Section \ref{sec:defn_artingroup}, we define the appropriate relations for our Artin group presentations. Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles. Section \ref{sec:main_result} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$. Finally, in Section \ref{sec:affine}, we will state a conjecture which could extend the main result to diagrams of affine type.\\

In the process of writing this paper, we became aware of related results obtained independently by Grant and Marsh in \cite{GM14} and Qiu in \cite{Q14}. Using different approaches, the two papers found relations for the Artin group in the simply-laced cases. However, their relations differ from the ones used in our paper, and our approach to the problem is more combinatorial than the more topological approaches found in \cite{Q14} and \cite{GM14}.
